Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
include new figures for inter-rater checks

@@

set.seed(23)
theme_set(theme_classic())
color_scheme_set(scheme = "gray")

@@

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value."}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black",
                 colour = "black") +
  xlab("Reproducibility score (%)")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```

@@

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

>>>>

```{r interRaterSD, echo=FALSE, message=FALSE, warning=FALSE}
ir %>%
  group_by(doi) %>%
  summarise(x = round(sd(reproducibility_score), 1)) %>%
  rename(`Standard Deviation` = x) %>%
  rename(DOI = doi) %>%
  flextable() %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Standard deviation of reproducibility scores for five articles evaluated by all five co-authors to check for differences in article ratings.")
```

@@

set.seed(23)

color_scheme_set(scheme = "gray")

@@

```{r irArtClass, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator classifications of (A) an articles focus being molecular techniques (TRUE/FALSE) and (B) an article's class (Fundamental/Applied). Where all five articles were scored by all five authors to check for agreement between the evaluations.", cache=FALSE, fig.env='figure'}

theme_set(theme_classic())
a <- ggplot(ir, aes(y = doi,
                      fill = molecular)) +
  geom_bar() +
  scale_fill_grey(name = "") +
  ylab("DOI") +
  xlab("Count") +
  ggtitle("Molecular Focus") +
  theme(legend.position = "top")

b <- ggplot(ir, aes(y = doi,
                      fill = art_class)) +
  geom_bar() +
  scale_fill_grey(name = "") +
  xlab("Count") +
  ylab("") +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  ggtitle("Article Class") +
  theme(legend.position = "top")

p <- (a | b)
p <- p + plot_annotation(tag_levels = "A",
                         title = "Evaluator agreement in article classifications")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```

```{r irCriteria, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Evaluator agreement for five articles scored for (A) software being properly cited, (B) software used being freely and openly available, (C) computational methods used, e.g. scripts or other self-written programs were freely and openly available and (D) data represented in the paper were freely and openly available. Note that one evaluator rated an article with computational methods available as 'NA', which is reflected in that article having only four evaluations for this criteria.", cache=FALSE, fig.env='figure'}
a <- ggplot(ir,
            aes(y = doi,
                x = software_cite)) +
  ylab("DOI") +
  xlab("") +
  xlim(c(0, 3)) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  geom_density_ridges() +
  ggtitle("Software Cited")

b <- ggplot(ir,
            aes(y = doi,
                x = software_avail)) +
  ylab("") +
  xlab("") +
  geom_density_ridges() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  xlim(c(0, 3)) +
  ggtitle("Software Available")

c <- ggplot(ir,
            aes(y = doi,
                x = comp_mthds_avail)) +
  geom_density_ridges() +
  ylab("DOI") +
  xlab("Score") +
  xlim(c(0, 3)) +
  ggtitle("Comp. Methods Available")

d <- ggplot(ir,
            aes(y = doi,
                x = data_avail)) +
  ylab("") +
  xlab("Score") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlim(c(0, 3)) +
  geom_density_ridges() +
  ggtitle("Data Available")

p <- (a | b) / (c | d)
p <- p + plot_annotation(tag_levels = "A",
                         title = "Evaluator agreement in article reproducibility criteria scoring")

```{r irReproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Overall reproducibility scores of five articles scored for evaluator agreement. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
p <- ggplot(ir,
            aes(y = doi,
                x = reproducibility_score)) +
  geom_density_ridges() +
  ggtitle("Inter-rater reproducibility score for five articles") +
  ylab("DOI") +
  xlab("Reproducibility Score (%)") +
  xlim(c(0, 100))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value.", cache=FALSE, fig.env='figure'}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black",
                 colour = "black") +
  xlab("Reproducibility score (%)")

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_7.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_7.eps"))
```
